\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.6in}
\addtolength{\textwidth}{1.2in}
\addtolength{\topmargin}{-0.95in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Section formatting
\titleformat{\section}{
  \vspace{-5pt}\bfseries\large\raggedright
}{}{0em}{}[\color{black}\titlerule \vspace{-4pt}]

% Reduce list spacing
\setlist[itemize]{itemsep=0.01pt, topsep=0pt, leftmargin=0.15in}

\newcommand{\resumeItem}[1]{
  \item\small{{#1}}
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{#4} \\
      \textit{\normalsize #3} & \normalsize #2 \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
    \end{tabular*}\vspace{-3pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeItemListEnd}{\end{itemize}}

\pdfgentounicode=1
% \linespread{1.045}
\begin{document}

%----------HEADING----------
\begin{center}
    {\fontsize{14pt}{16pt}\selectfont\textbf{Deepanjay Nandal}} \\ \vspace{2pt}
    \normalsize +1 (602) 790-9401 $|$ \href{mailto:deepanjay.nandal12@gmail.com}{deepanjay.nandal12@gmail.com} $|$ 
    \href{https://www.linkedin.com/in/deepanjay-nandal/}{linkedin.com/in/deepanjay} $|$
    \href{https://github.com/DeepanjayNandal}{github.com/Deepanjay}
\end{center}

\vspace{-3pt}

%-----------EDUCATION-----------
\vspace{-9pt}
\section{Education}
\resumeSubHeadingListStart
  \resumeSubheading
    {Arizona State University}{Arizona, USA}
    {Masters of Science in Computer Software Engineering}{August 2024 - May 2026}
  \resumeSubheading
    {Vellore Institute Of Technology}{Tamil Nadu, India}
    {Bachelor of Technology in Information Technology}{July 2017 - July 2021}
\resumeSubHeadingListEnd

%-----------TECHNICAL SKILLS-----------
\section{Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
  \small{\item{
    \textbf{Programming Languages}{: Java, Python, C++, JavaScript, Dart, TypeScript, SQL, Bash} \\
    \textbf{Mobile \& Web Development}{: Flutter, React, Next.js, Tailwind CSS} \\
    \textbf{Backend Development}{: Flask, Node.js, Express.js, REST APIs, JWT Authentication} \\
    \textbf{Security \& Reverse Engineering}{: Android Security, AOSP, Frida, Ghidra, ClusterFuzz, Assembly Analysis, Static/Dynamic Analysis} \\
    \textbf{Testing \& Automation}{: AndroidJUnitRunner, JUnit, UIAutomator, Tradefed, memutils, Logging, Triage Reports} \\
    \textbf{Tools \& Platforms}{: Git, Android Studio, ADB, IDA Pro, VS Code, IntelliJ, Postman, Xcode}
    \textbf{Databases \& Data Tools}{: MongoDB, SQLite, Firebase, Pandas, NumPy, Scikit-learn, SPARQL} \\
    \textbf{Cloud \& DevOps}{: Vercel, Microsoft Azure, Docker, GitHub Actions, CI/CD Fundamentals} \\
    \textbf{Software Architecture}{: Clean Architecture, Repository Pattern, Provider Pattern, SOLID Principles} \\
    \textbf{Additional}{: WebRTC, OAuth2.0, RBAC, Sentry, Secure Storage, Responsive UI Design}
  }}
\end{itemize}

%-----------EXPERIENCE-----------
\vspace{-9pt}
\section{Experience}
\resumeSubHeadingListStart

  \resumeSubheading
  {Ittiam Systems Pvt Ltd}{Bangalore, India}
  {Senior Software Engineer}{March 2022 – June 2024}
  \resumeItemListStart
    \resumeItem{Built and maintained over 40 Compatibility Test Suites for Google’s Android Security Test Suite, integrating them into AOSP to help validate security patches and ensure compliance.}
    \resumeItem{Introduced reverse engineering workflows with Ghidra and Frida, increasing bug identification by 150\% and enabling dynamic inspection of previously inaccessible vulnerabilities.}
    \resumeItem{Automated crash reproduction and triage scripts using ClusterFuzz and Python, reducing duplicate crash reports by 75\% and accelerating patch analysis.}
    \resumeItem{Designed and implemented memutils for out-of-memory error detection, expanding test coverage and earning recognition with a “Best Employee” award.}
    \resumeItem{Wrote triage reports with control flow breakdowns and insights for over 50 bugs, helping accelerate patch verification.}
    \resumeItem{Analyzed Assembly Code from OEMs (Lenovo, Samsung, Asus) as part of Google’s Build Test Suite to assess patch status and accelerate partner security updates.}
  \resumeItemListEnd

  \resumeSubheading
  {Accenture}{Pune, India}
  {Associate Application Developer}{November 2021 – March 2022}
  \resumeItemListStart
    \resumeItem{Completed Java training covering OOP, database connectivity, and concurrency using real-world simulations.}
    \resumeItem{Assisted with feature rollouts and integration while contributing to Git workflows and code reviews during Agile sprints.}
  \resumeItemListEnd

\resumeSubHeadingListEnd
\vspace{-9pt}
%-----------PROJECTS-----------
\section{Projects}
\resumeSubHeadingListStart

\resumeProjectHeading
  {\textbf{CaseTally – Cross-Platform Secure Communication Platform for Legal Use Cases}}{}
  \resumeItemListStart
    \resumeItem{Developed a privacy-focused real-time video and chat system over WebRTC, linking QR-based ECDH key exchange and XChaCha20 encryption with offline messaging support.}
    \resumeItem{Created a lightweight signaling protocol to support persistent sessions, reconnections, and offline message queuing with sync-on-reconnect.}
    \resumeItem{Structured contact and session lifecycle logic around role-based access control with the Repository Pattern and Provider, following Clean Architecture principles to improve modularity and testability.}
    \resumeItem{Built the backend with Flask and MongoDB, applying JWT authentication and encrypted client-side data handling through protected local storage.}
    \resumeItem{Enabled runtime observability and real-time error tracking via Sentry, connected to structured logs and crash reports.}
    \resumeItem{\textbf{Skills}: Flutter, Dart, WebRTC, Flask, MongoDB, JWT, XChaCha20, ECDH, Provider, Sentry, Secure Storage}
  \resumeItemListEnd


\resumeProjectHeading
  {\textbf{Nutritional Calculator Web App}}{}
  \resumeItemListStart
    \resumeItem{Designed full-stack app for real-time nutrition analysis via SPARQL-backed knowledge graph.}
    \resumeItem{Leveraged semantic search and RDF mapping via Node.js backend with SPARQL endpoints.}
    \resumeItem{Delivered responsive, low-latency UI with Next.js, Tailwind CSS, async APIs, and non-blocking data flows.}
    \resumeItem{\textbf{Skills}: Node.js, Next.js, Tailwind CSS, SPARQL, Semantic Web, REST APIs, Vercel}
  \resumeItemListEnd

\resumeSubHeadingListEnd

\vspace{-9pt}

\end{document}
